\documentclass[oneside, openany]{memoir}
\usepackage[leqno]{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{thmtools}
\usepackage{xspace}

\usepackage{tgpagella}
\usepackage[sc]{mathpazo}
\usepackage{microtype}

\chapterstyle{companion}

\swapnumbers
\declaretheoremstyle[headfont = \scshape, bodyfont = \normalfont, qed = \qedsymbol]{foag}
\declaretheorem[style = foag, numberwithin = section]{exercise}
\renewcommand{\theexercise}{\textbf{\arabic{chapter}.\arabic{section}.\Alph{exercise}}}

\newcommand\foreign[1]{\emph{#1}}
\newcommand\eg{\foreign{e.g.}}
\newcommand\Eg{\foreign{E.g.}}
\newcommand\ie{\foreign{i.e.}\xspace}
\newcommand\Ie{\foreign{I.e.}}
\newcommand\vs{\foreign{vs.~}}
\newcommand\cf{\foreign{cf.\xspace}}
\newcommand\resp{\foreign{resp.}}
\newcommand\etc{\foreign{etc.}}

\newcommand\category[1]{\mathsf{#1}}

\DeclareMathOperator\Mor{Mor}

\title{Solutions to Foundations of Algebraic Geometry}
\author{Pieter Belmans}

\begin{document}

\maketitle

\begin{abstract}
  These notes contain my solutions to Ravi Vakil's Foundations of Algebraic Geometry. For more information I refer you to the official website/blog (\url{http://math216.wordpress.com/}) and the page with the actual notes (\url{http://math.stanford.edu/~vakil/216blog/}).
  
  The solutions are provided as is. I don't claim these to be correct or well written (although I certainly intend them to be for my own benefit). If you encounter any flagrant mistakes, you can contact me by e-mail (\url{pieterbelmans@gmail.com}) or add a patch to the GitHub repository at \url{https://github.com/pbelmans/math216}. Please do so by the way, preferably by submitting patches.

  As the notes are still being written when I started writing up these solutions and there may be changes to the numbering system upcoming: I am using the June 27 version. If I am still interested in these exercises when a final version is posted, I might edit in possible changes.
\end{abstract}

\clearpage

\tableofcontents*


\chapter{Introduction}
There are no exercises in this chapter.


\part{Preliminaries}

\chapter{Some category theory}
\input{ch2.tex}

\chapter{Sheaves}
\input{ch3.tex}


\part{Schemes}

\chapter{Toward affine schemes}
\input{ch4.tex}

\chapter{The structure sheaf and the definition of schemes in general}
\input{ch5.tex}

\chapter{Some properties of schemes}
\input{ch6.tex}

\part{Morphisms of schemes}

\part{Quasicoherent sheaves}

\part{More}
\end{document}
